---
title: "Identifying Unique Claims"
author: "Spiro Stilianoudakis"
date: "August 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
library(sas7bdat)
library(lubridate)
library(tidyr)
```

# Set working directory

```{r}
setwd("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data")
```

# Reading in pregnancy claims data

```{r}
claims <- read.xlsx("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/Pregnant_claims_2015_2018.xlsx",
                    sheet = "Pregnant_claims_2015_2018",
                    startRow = 1,
                    colNames = TRUE,
                    na.strings = "",
                    detectDates = TRUE)

claims <- claims[order(claims$SRECIP, decreasing = FALSE),]

dim(claims)
#184976     41

length(unique(claims$SRECIP)) #17485
length(unique(claims$CLAIM_NUMBER)) #64830
```

# Reading in cleaned eligibility data

```{r}
eligibility <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/ffs_mco_2015_2016_2017_2018.rds")
dim(eligibility) #103204    156
```

# Joining dental claims with eligibility data

```{r}
cols <- c("srecip", "Overall_Region", "HEALTH_PLANNING_DISTRICT", "HEALTH_PLANNING_REGION", "Overall_Citizen", "Overall_Race", "Overall_Age_at_earliest_enrollment")

claims <- left_join(claims, eligibility[,which(names(eligibility) %in% cols)], by = c("SRECIP" = "srecip"))

#remove claims that are not in eligibility
claims <- claims[which(claims$SRECIP %in% eligibility$srecip),]
dim(claims) #179518     47

#creating variables
#race
claims$Race[which(claims$Race=="American Indian or Alaskan Native" | claims$Race=="Asian or Pacific Islander")] <- "Native American/Asian"
claims$Race[which(claims$Race=="Caucasian")] <- "White"
claims$Race[which(claims$Race=="Other/Missing")] <- "Other"

#FY
claims$FY_2015 <- ifelse(claims$FY=="2015", 1, 0)
claims$FY_2016 <- ifelse(claims$FY=="2016", 1, 0)
claims$FY_2017 <- ifelse(claims$FY=="2017", 1, 0)
claims$FY_2018 <- ifelse(claims$FY=="2018", 1, 0)

#create age category from eligibility
claims$age_cat_eligibility <- ifelse(claims$Overall_Age_at_earliest_enrollment < 21, "<21",
                                   ifelse(claims$Overall_Age_at_earliest_enrollment>= 21 & claims$Overall_Age_at_earliest_enrollment < 31, "21-30",
                                          ifelse(claims$Overall_Age_at_earliest_enrollment >= 31 & claims$Overall_Age_at_earliest_enrollment < 41, "31-40",
                                                 ifelse(claims$Overall_Age_at_earliest_enrollment >= 41 & claims$Overall_Age_at_earliest_enrollment < 51, "41-50", ">50"))))
claims$age_cat_eligibility <- factor(claims$age_cat_eligibility, levels=c("<21", "21-30", "31-40", "41-50", ">50"))

##D0100-D0999 DIAGNOSTIC
##D1000-D1999 PREVENTIVE
##D2000-D2999 RESTORATIVE
##D3000-D3999 ENDODONTICS
##D4000-D4999 PERIODONTICS
##D5000-D5899 PROSTHODONTICS
##D5900-D5999 MAXILLOFACIAL PROSTHETICS
##D6000-D6199 IMPLANT SERVICES
##D6200-D6999 PROSTHODONTICS
##D7000-D7999 ORAL & MAXILLOFACIAL SURGERY
##D8000-D8999 ORTHODONTICS
##D9000-D9999 ADJUNCTIVE GENERAL SERVICES

claims$CDT_category <- ifelse(claims$proc_code %in% paste0(0,c(100:999)), "DIAGNOSTIC",
                              ifelse(claims$proc_code %in% c(1000:1999), "PREVENTIVE",
                                     ifelse(claims$proc_code %in% c(2000:2999), "RESTORATIVE",
                                            ifelse(claims$proc_code %in% c(3000:3999), "ENDODONTICS",
                                                   ifelse(claims$proc_code %in% c(4000:4999), "PERIODONTICS",
                                                          ifelse(claims$proc_code %in% c(5000:5899), "PROSTHODONTICS", 
                                                                 ifelse(claims$proc_code %in% c(5900:5999), "MAXILLOFACIAL PROSTHETICS",
                                                                        ifelse(claims$proc_code %in% c(6000:6199), "IMPLANT SERVICES",
                                                                               ifelse(claims$proc_code %in% c(6200:6999), "PROSTHODONTICS",
                                                                                      ifelse(claims$proc_code %in% c(7000:7999), "ORAL & MAXILLOFACIAL SURGERY",
                                                                                             ifelse(claims$proc_code %in% c(8000:8999), "ORTHODONTICS",
                                                                                                    ifelse(claims$proc_code %in% c(9000:9999), "ADJUNCTIVE GENERAL SERVICES", "UNKNOWN"))))))))))))

```

# Identifying unique claims

## Claims with tooth number

### Removing duplicates based on: claim #, proc code, service date, tooth number

```{r}
claims_tooth <- claims[!is.na(claims$Tooth_Number),]
dim(claims_tooth) #118618     53
table(claims_tooth$Tooth_Number, exclude = "ifany")

claims_tooth <- claims_tooth[order(claims_tooth$CLAIM_NUMBER, decreasing = TRUE),]

head(claims_tooth[,c("CLAIM_NUMBER", "SRECIP", "SERVICE_DATE", "AMOUNT_PAID", "proc_code", "Tooth_Number", "billing_prov_NPI", "CDT_category", "FY_2015" ,"FY_2016" ,"FY_2017", "FY_2018")])

claims_nodup_tooth <- claims_tooth[!(duplicated(claims_tooth[,c("CLAIM_NUMBER", "proc_code", "SERVICE_DATE", "Tooth_Number")])),]
dim(claims_nodup_tooth) #118616    53

```


## Claims with no tooth number

### Removing duplicates based on: claim #, proc code, service date, amount paid

```{r}
claims_no_tooth <- claims[is.na(claims$Tooth_Number),]
dim(claims_no_tooth) #60900    53
table(claims_no_tooth$Tooth_Number, exclude = "ifany")

claims_no_tooth <- claims_no_tooth[order(claims_no_tooth$CLAIM_NUMBER, decreasing = TRUE),]

head(claims_no_tooth[,c("CLAIM_NUMBER", "SRECIP", "SERVICE_DATE", "AMOUNT_PAID", "proc_code", "Tooth_Number", "billing_prov_NPI", "CDT_category", "FY_2015" ,"FY_2016" ,"FY_2017", "FY_2018")])

claims_nodup_no_tooth <- claims_no_tooth[!(duplicated(claims_no_tooth[,c("CLAIM_NUMBER", "proc_code", "SERVICE_DATE", "AMOUNT_PAID")])),]
dim(claims_nodup_no_tooth) #60900    53

```

## Combining the two data sets

```{r}
unique_claims <- rbind.data.frame(claims_nodup_no_tooth, claims_nodup_tooth)
dim(unique_claims) #179516     53

```

# Claim level data

```{r}
claim_level <- unique_claims[,c("CLAIM_NUMBER", "SRECIP", "SERVICE_DATE", "AMOUNT_PAID", "proc_code", "Tooth_Number", "billing_prov_NPI", "CDT_category", "FY_2015" ,"FY_2016" ,"FY_2017", "FY_2018")]

claim_level <- claim_level[order(claim_level$CLAIM_NUMBER, decreasing = TRUE),]

```

## Overall

```{r}
#total number
dim(claim_level)

#cdt category
table(claim_level$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level$CDT_category, exclude = "ifany")), 3)
```

## 2015

```{r}
claim_level_2015 <- claim_level[which(claim_level$FY_2015==1),]
 
#total number
dim(claim_level_2015)

#cdt category
table(claim_level_2015$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2015$CDT_category, exclude = "ifany")), 3)

```

## 2016

```{r}
claim_level_2016 <- claim_level[which(claim_level$FY_2016==1),]
 
#total number
dim(claim_level_2016)

#cdt category
table(claim_level_2016$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2016$CDT_category, exclude = "ifany")), 3)

```

## 2017

```{r}
claim_level_2017 <- claim_level[which(claim_level$FY_2017==1),]
 
#total number
dim(claim_level_2017)

#cdt category
table(claim_level_2017$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2017$CDT_category, exclude = "ifany")), 3)

```

## 2018

```{r}
claim_level_2018 <- claim_level[which(claim_level$FY_2018==1),]
 
#total number
dim(claim_level_2018)

#cdt category
table(claim_level_2018$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2018$CDT_category, exclude = "ifany")), 3)

```

# Unique claim level data

```{r}
claim_level_no_dup <- claim_level[!duplicated(claim_level$CLAIM_NUMBER),]
dim(claim_level_no_dup) #62955
```

## Overall

```{r}
#total number
dim(claim_level_no_dup)

#cdt category
table(claim_level_no_dup$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_no_dup$CDT_category, exclude = "ifany")), 3)
```

## 2015

```{r}
claim_level_no_dup_2015 <- claim_level_no_dup[which(claim_level_no_dup$FY_2015==1),]
 
#total number
dim(claim_level_no_dup_2015)

#cdt category
table(claim_level_no_dup_2015$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_no_dup_2015$CDT_category, exclude = "ifany")), 3)
```

## 2016

```{r}
claim_level_no_dup_2016 <- claim_level_no_dup[which(claim_level_no_dup$FY_2016==1),]
 
#total number
dim(claim_level_no_dup_2016)

#cdt category
table(claim_level_no_dup_2016$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_no_dup_2016$CDT_category, exclude = "ifany")), 3)

```

## 2017

```{r}
claim_level_no_dup_2017 <- claim_level_no_dup[which(claim_level_no_dup$FY_2017==1),]
 
#total number
dim(claim_level_no_dup_2017)

#cdt category
table(claim_level_no_dup_2017$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_no_dup_2017$CDT_category, exclude = "ifany")), 3)
```

## 2018

```{r}
claim_level_no_dup_2018 <- claim_level_no_dup[which(claim_level_no_dup$FY_2018==1),]
 
#total number
dim(claim_level_no_dup_2018)

#cdt category
table(claim_level_no_dup_2018$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_no_dup_2018$CDT_category, exclude = "ifany")), 3)
```


# Patient level data

```{r}
patient_level <- unique_claims[!duplicated(unique_claims[,c("SRECIP")]),]
dim(patient_level) #16891    52

#Number of claims per patient
num_claims <- unique_claims %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()

#Number of visits  per patient
num_visits <- unique_claims[!duplicated(unique_claims[,c("SRECIP","SERVICE_DATE")]),] %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()

#Total Cost per patient 
totc <- unique_claims %>%
  dplyr::group_by(SRECIP) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))

patient_level$Num_claims <- num_claims$n
patient_level$Num_visits <- num_visits$n
patient_level$Total_cost <- totc$Total_Cost

```

## Overall

```{r}
dim(patient_level)

#Number of claims per patient
mean(patient_level$Num_claims)
sd(patient_level$Num_claims)

#Number of visits per patient
mean(patient_level$Num_visits)
sd(patient_level$Num_visits)

#Costs per patient
mean(patient_level$Total_cost)
sd(patient_level$Total_cost)

#age

#age category

#race

#citizenship

#region

#hpd

#hpr
```


## 2015

```{r}
patient_level_2015 <- patient_level[which(patient_level$FY_2015==1),]
dim(patient_level_2015)

#Number of claims per patient
mean(patient_level_2015$Num_claims)
sd(patient_level_2015$Num_claims)

#Number of visits per patient
mean(patient_level_2015$Num_visits)
sd(patient_level_2015$Num_visits)

#Costs per patient
mean(patient_level_2015$Total_cost)
sd(patient_level_2015$Total_cost)

#age
mean(patient_level_2015$Overall_Age_at_earliest_enrollment)
sd(patient_level_2015$Overall_Age_at_earliest_enrollment)

#age category
table(patient_level_2015$age_cat_eligibility, exclude = "ifany")
prop.table(table(patient_level_2015$age_cat_eligibility, exclude = "ifany"))

#race
table(patient_level_2015$Overall_Race, exclude = "ifany")
prop.table(table(patient_level_2015$Overall_Race, exclude = "ifany"))

#citizenship
table(patient_level_2015$Overall_Citizen, exclude = "ifany")
prop.table(table(patient_level_2015$Overall_Citizen, exclude = "ifany"))

#region
table(patient_level_2015$Overall_Region, exclude = "ifany")
prop.table(table(patient_level_2015$Overall_Region, exclude = "ifany"))

#hpd
table(patient_level_2015$HEALTH_PLANNING_DISTRICT, exclude = "ifany")
prop.table(table(patient_level_2015$HEALTH_PLANNING_DISTRICT, exclude = "ifany"))

#hpr
table(patient_level_2015$HEALTH_PLANNING_REGION, exclude = "ifany")
prop.table(table(patient_level_2015$HEALTH_PLANNING_REGION, exclude = "ifany"))


```


## 2016

```{r}
patient_level_2016 <- patient_level[which(patient_level$FY_2016==1),]
dim(patient_level_2016)

#Number of claims per patient
mean(patient_level_2016$Num_claims)
sd(patient_level_2016$Num_claims)

#Number of visits per patient
mean(patient_level_2016$Num_visits)
sd(patient_level_2016$Num_visits)

#Costs per patient
mean(patient_level_2016$Total_cost)
sd(patient_level_2016$Total_cost)

#age
mean(patient_level_2016$Overall_Age_at_earliest_enrollment)
sd(patient_level_2016$Overall_Age_at_earliest_enrollment)

#age category
table(patient_level_2016$age_cat_eligibility, exclude = "ifany")
prop.table(table(patient_level_2016$age_cat_eligibility, exclude = "ifany"))

#race
table(patient_level_2016$Overall_Race, exclude = "ifany")
prop.table(table(patient_level_2016$Overall_Race, exclude = "ifany"))

#citizenship
table(patient_level_2016$Overall_Citizen, exclude = "ifany")
prop.table(table(patient_level_2016$Overall_Citizen, exclude = "ifany"))

#region
table(patient_level_2016$Overall_Region, exclude = "ifany")
prop.table(table(patient_level_2016$Overall_Region, exclude = "ifany"))

#hpd
table(patient_level_2016$HEALTH_PLANNING_DISTRICT, exclude = "ifany")
prop.table(table(patient_level_2016$HEALTH_PLANNING_DISTRICT, exclude = "ifany"))

#hpr
table(patient_level_2016$HEALTH_PLANNING_REGION, exclude = "ifany")
prop.table(table(patient_level_2016$HEALTH_PLANNING_REGION, exclude = "ifany"))



```


## 2017

```{r}
patient_level_2017 <- patient_level[which(patient_level$FY_2017==1),]
dim(patient_level_2017)

#Number of claims per patient
mean(patient_level_2017$Num_claims)
sd(patient_level_2017$Num_claims)

#Number of visits per patient
mean(patient_level_2017$Num_visits)
sd(patient_level_2017$Num_visits)

#Costs per patient
mean(patient_level_2017$Total_cost)
sd(patient_level_2017$Total_cost)

#age
mean(patient_level_2017$Overall_Age_at_earliest_enrollment)
sd(patient_level_2017$Overall_Age_at_earliest_enrollment)

#age category
table(patient_level_2017$age_cat_eligibility, exclude = "ifany")
prop.table(table(patient_level_2017$age_cat_eligibility, exclude = "ifany"))

#race
table(patient_level_2017$Overall_Race, exclude = "ifany")
prop.table(table(patient_level_2017$Overall_Race, exclude = "ifany"))

#citizenship
table(patient_level_2017$Overall_Citizen, exclude = "ifany")
prop.table(table(patient_level_2017$Overall_Citizen, exclude = "ifany"))

#region
table(patient_level_2017$Overall_Region, exclude = "ifany")
prop.table(table(patient_level_2017$Overall_Region, exclude = "ifany"))

#hpd
table(patient_level_2017$HEALTH_PLANNING_DISTRICT, exclude = "ifany")
prop.table(table(patient_level_2017$HEALTH_PLANNING_DISTRICT, exclude = "ifany"))

#hpr
table(patient_level_2017$HEALTH_PLANNING_REGION, exclude = "ifany")
prop.table(table(patient_level_2017$HEALTH_PLANNING_REGION, exclude = "ifany"))


```


## 2018

```{r}
patient_level_2018 <- patient_level[which(patient_level$FY_2018==1),]
dim(patient_level_2018)

#Number of claims per patient
mean(patient_level_2018$Num_claims)
sd(patient_level_2018$Num_claims)

#Number of visits per patient
mean(patient_level_2018$Num_visits)
sd(patient_level_2018$Num_visits)

#Costs per patient
mean(patient_level_2018$Total_cost)
sd(patient_level_2018$Total_cost)

#age
mean(patient_level_2018$Overall_Age_at_earliest_enrollment)
sd(patient_level_2018$Overall_Age_at_earliest_enrollment)

#age category
table(patient_level_2018$age_cat_eligibility, exclude = "ifany")
prop.table(table(patient_level_2018$age_cat_eligibility, exclude = "ifany"))

#race
table(patient_level_2018$Overall_Race, exclude = "ifany")
prop.table(table(patient_level_2018$Overall_Race, exclude = "ifany"))

#citizenship
table(patient_level_2018$Overall_Citizen, exclude = "ifany")
prop.table(table(patient_level_2018$Overall_Citizen, exclude = "ifany"))

#region
table(patient_level_2018$Overall_Region, exclude = "ifany")
prop.table(table(patient_level_2018$Overall_Region, exclude = "ifany"))

#hpd
table(patient_level_2018$HEALTH_PLANNING_DISTRICT, exclude = "ifany")
prop.table(table(patient_level_2018$HEALTH_PLANNING_DISTRICT, exclude = "ifany"))

#hpr
table(patient_level_2018$HEALTH_PLANNING_REGION, exclude = "ifany")
prop.table(table(patient_level_2018$HEALTH_PLANNING_REGION, exclude = "ifany"))


```


# Provider Level data

```{r}
#finding number of invalid provider ids
head(table(sort(unique_claims$billing_prov_NPI)))
#         . 1003005547 1003088030 1003095266 1003240276 1003251992 
#       684        112       1380          6          5        120 

#break up billing provider name into first and last
providers <- extract(unique_claims, BillIng_Provider_name, c("ProviderLastName", "ProviderFirstName"), "([^ ]+) (.*)")
providers$ProviderFirstName <- toupper(providers$ProviderFirstName)
providers$ProviderLastName <- toupper(providers$ProviderLastName)

head(providers[which(providers$billing_prov_NPI=="         ."), c("CLAIM_NUMBER", "AMOUNT_PAID", "proc_code", "new_service_date", "SRECIP", "SERVICING_PROVIDER_NPI", "billing_prov_NPI", "ProviderFirstName", "ProviderLastName")])

invalid_npi <- providers[which(providers$billing_prov_NPI=="         ."), c("CLAIM_NUMBER", "AMOUNT_PAID", "proc_code", "new_service_date", "SRECIP", "SERVICING_PROVIDER_NPI", "billing_prov_NPI", "ProviderFirstName", "ProviderLastName")]

table(invalid_npi$ProviderFirstName, exclude = "ifany")
table(invalid_npi$ProviderLastName, exclude = "ifany")

#fill in missing billing provider npi using name joined from all_dental_providers

all_dental_providers <- read.xlsx("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/all_dental_providers.xlsx",
                    sheet = "all_dental_providers",
                    startRow = 1,
                    colNames = TRUE,
                    na.strings = "",
                    detectDates = TRUE)
dim(all_dental_providers)
#24208    10

all_dental_providers <- all_dental_providers[order(all_dental_providers$PTL_NPI_ID),]
all_dental_providers <- all_dental_providers[!duplicated(all_dental_providers[,2:3]),]
dim(all_dental_providers)
#6914   10

providers2 <- left_join(providers, all_dental_providers[,1:3], by = c("ProviderFirstName" = "PTL_P_FIRST", "ProviderLastName" = "PTL_P_LAST"))
dim(providers2)
#179516     55

providers2$billing_prov_NPI[which(providers2$billing_prov_NPI=="         ." & !is.na(providers2$PTL_NPI_ID))] <- providers2$PTL_NPI_ID[which(providers2$billing_prov_NPI=="         ." & !is.na(providers2$PTL_NPI_ID))]


length(which(providers2$billing_prov_NPI=="         .")) #85

#remove missing provider ids
providers2 <- providers2[-which(providers2$billing_prov_NPI=="         ."),]
dim(providers2) #179431    55

#some billing ids don't match between claims and provider data sets
providers2[which(providers2$ProviderFirstName=="SEBASTIAN" & providers2$ProviderLastName=="BOURONCLE"),c("ProviderFirstName", "ProviderLastName", "billing_prov_NPI", "PTL_NPI_ID")]
##Ex. SEBASTIAN        BOURONCLE; 1740667799 1932245511
##this person actually has two provider ids in the provider dataset

provider_level <- providers2[!duplicated(providers2$billing_prov_NPI),]
```


## Overall

```{r}
#unique providers
dim(provider_level) 

#Number of patients per provider
num_pats <- providers2 %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()
mean(num_pats$n)
sd(num_pats$n)

#Cost of services per provider
totc <- providers2 %>%
  dplyr::group_by(billing_prov_NPI) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
mean(totc$Total_Cost)
sd(totc$Total_Cost)
ggplot()+geom_histogram(aes(totc$Total_Cost), bins = 50)+
  scale_x_continuous(breaks=c(0,200000,400000,600000),
                     labels=c("0","200000", "400000", "600000"))+
  xlab("Cost of Services per Provider")+
  ylab("Count")+
  theme_bw()

```

## 2015

```{r}
provider_level_2015 <- provider_level[which(provider_level$FY_2015==1),]

#Number of unique providers
dim(provider_level_2015)

#Number of patients per provider
num_pats <- providers2[which(providers2$FY_2015==1),] %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()
mean(num_pats$n)
sd(num_pats$n)

#Cost of services per provider
totc <- providers2[which(providers2$FY_2015==1),] %>%
  dplyr::group_by(billing_prov_NPI) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
mean(totc$Total_Cost)
sd(totc$Total_Cost)
ggplot()+geom_histogram(aes(totc$Total_Cost), bins = 50)+
  #scale_x_continuous(breaks=c(0,200000,400000,600000),
  #                   labels=c("0","200000", "400000", "600000"))+
  xlab("Cost of Services per Provider")+
  ylab("Count")+
  theme_bw()

```

## 2016

```{r}
provider_level_2016 <- provider_level[which(provider_level$FY_2016==1),]

#Number of unique providers
dim(provider_level_2016)

#Number of patients per provider
num_pats <- providers2[which(providers2$FY_2016==1),] %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()
mean(num_pats$n)
sd(num_pats$n)

#Cost of services per provider
totc <- providers2[which(providers2$FY_2016==1),] %>%
  dplyr::group_by(billing_prov_NPI) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
mean(totc$Total_Cost)
sd(totc$Total_Cost)
ggplot()+geom_histogram(aes(totc$Total_Cost), bins = 50)+
  #scale_x_continuous(breaks=c(0,200000,400000,600000),
  #                   labels=c("0","200000", "400000", "600000"))+
  xlab("Cost of Services per Provider")+
  ylab("Count")+
  theme_bw()

```


## 2017

```{r}
provider_level_2017 <- provider_level[which(provider_level$FY_2017==1),]

#Number of unique providers
dim(provider_level_2017)

#Number of patients per provider
num_pats <- providers2[which(providers2$FY_2017==1),] %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()
mean(num_pats$n)
sd(num_pats$n)

#Cost of services per provider
totc <- providers2[which(providers2$FY_2017==1),] %>%
  dplyr::group_by(billing_prov_NPI) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
mean(totc$Total_Cost)
sd(totc$Total_Cost)
ggplot()+geom_histogram(aes(totc$Total_Cost), bins = 50)+
  #scale_x_continuous(breaks=c(0,200000,400000,600000),
  #                   labels=c("0","200000", "400000", "600000"))+
  xlab("Cost of Services per Provider")+
  ylab("Count")+
  theme_bw()

```


## 2018

```{r}
provider_level_2018 <- provider_level[which(provider_level$FY_2018==1),]

#Number of unique providers
dim(provider_level_2018)

#Number of patients per provider
num_pats <- providers2[which(providers2$FY_2018==1),] %>% 
  dplyr::group_by(SRECIP) %>%
  dplyr::count()
mean(num_pats$n)
sd(num_pats$n)

#Cost of services per provider
totc <- providers2[which(providers2$FY_2018==1),] %>%
  dplyr::group_by(billing_prov_NPI) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
mean(totc$Total_Cost)
sd(totc$Total_Cost)
ggplot()+geom_histogram(aes(totc$Total_Cost), bins = 50)+
  #scale_x_continuous(breaks=c(0,200000,400000,600000),
  #                   labels=c("0","200000", "400000", "600000"))+
  xlab("Cost of Services per Provider")+
  ylab("Count")+
  theme_bw()

```

