---
title: "Dentistry Claims RA Project"
subtitle: "Pregnancy Claims Data"
author: "Spiro Stilianoudakis"
date: "May 10, 2019"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '1'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
library(sas7bdat)
library(lubridate)
```

# Set working directory

```{r}
setwd("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data")
```

# Reading in pregnancy claims data

```{r}
claims <- read.xlsx("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/Pregnant_claims_2015_2018.xlsx",
                    sheet = "Pregnant_claims_2015_2018",
                    startRow = 1,
                    colNames = TRUE,
                    na.strings = "",
                    detectDates = TRUE)

claims <- claims[order(claims$SRECIP, decreasing = FALSE),]

dim(claims)
#184976     41

length(unique(claims$SRECIP)) #17485
length(unique(claims$CLAIM_NUMBER)) #64830
```

# Reading in cleaned eligibility data

```{r}
eligibility <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/ffs_mco_2015_2016_2017_2018.rds")
dim(eligibility) #103204    156
```

# Joining dental claims with eligibility data

```{r}
cols <- c("srecip", "Overall_Region", "HEALTH_PLANNING_DISTRICT", "HEALTH_PLANNING_REGION", "Overall_Citizen", "Overall_Race", "Overall_Age_at_earliest_enrollment")

claims <- left_join(claims, eligibility[,which(names(eligibility) %in% cols)], by = c("SRECIP" = "srecip"))

#remove claims that are not in eligibility
claims <- claims[which(claims$SRECIP %in% eligibility$srecip),]
dim(claims) #179518     47
```

# Creating variables

```{r}
#CDT code category
##D0100-D0999 DIAGNOSTIC
##D1000-D1999 PREVENTIVE
##D2000-D2999 RESTORATIVE
##D3000-D3999 ENDODONTICS
##D4000-D4999 PERIODONTICS
##D5000-D5899 PROSTHODONTICS
##D5900-D5999 MAXILLOFACIAL PROSTHETICS
##D6000-D6199 IMPLANT SERVICES
##D6200-D6999 PROSTHODONTICS
##D7000-D7999 ORAL & MAXILLOFACIAL SURGERY
##D8000-D8999 ORTHODONTICS
##D9000-D9999 ADJUNCTIVE GENERAL SERVICES

claims$CDT_category <- ifelse(claims$proc_code %in% paste0(0,c(100:999)), "DIAGNOSTIC",
                              ifelse(claims$proc_code %in% c(1000:1999), "PREVENTIVE",
                                     ifelse(claims$proc_code %in% c(2000:2999), "RESTORATIVE",
                                            ifelse(claims$proc_code %in% c(3000:3999), "ENDODONTICS",
                                                   ifelse(claims$proc_code %in% c(4000:4999), "PERIODONTICS",
                                                          ifelse(claims$proc_code %in% c(5000:5899), "PROSTHODONTICS", 
                                                                 ifelse(claims$proc_code %in% c(5900:5999), "MAXILLOFACIAL PROSTHETICS",
                                                                        ifelse(claims$proc_code %in% c(6000:6199), "IMPLANT SERVICES",
                                                                               ifelse(claims$proc_code %in% c(6200:6999), "PROSTHODONTICS",
                                                                                      ifelse(claims$proc_code %in% c(7000:7999), "ORAL & MAXILLOFACIAL SURGERY",
                                                                                             ifelse(claims$proc_code %in% c(8000:8999), "ORTHODONTICS",
                                                                                                    ifelse(claims$proc_code %in% c(9000:9999), "ADJUNCTIVE GENERAL SERVICES", "UNKNOWN"))))))))))))

#create age category
claims$age_cat <- ifelse(claims$age_at_procedure < 21, "<21",
                                   ifelse(claims$age_at_procedure>= 21 & claims$age_at_procedure < 31, "21-30",
                                          ifelse(claims$age_at_procedure >= 31 & claims$age_at_procedure < 41, "31-40",
                                                 ifelse(claims$age_at_procedure >= 41 & claims$age_at_procedure < 51, "41-50", ">50"))))
claims$age_cat <- factor(claims$age_cat, levels=c("<21", "21-30", "31-40", "41-50", ">50"))

#create age category from eligibility
claims$age_cat_eligibility <- ifelse(claims$Overall_Age_at_earliest_enrollment < 21, "<21",
                                   ifelse(claims$Overall_Age_at_earliest_enrollment>= 21 & claims$Overall_Age_at_earliest_enrollment < 31, "21-30",
                                          ifelse(claims$Overall_Age_at_earliest_enrollment >= 31 & claims$Overall_Age_at_earliest_enrollment < 41, "31-40",
                                                 ifelse(claims$Overall_Age_at_earliest_enrollment >= 41 & claims$Overall_Age_at_earliest_enrollment < 51, "41-50", ">50"))))
claims$age_cat_eligibility <- factor(claims$age_cat_eligibility, levels=c("<21", "21-30", "31-40", "41-50", ">50"))


#race
claims$Race[which(claims$Race=="American Indian or Alaskan Native" | claims$Race=="Asian or Pacific Islander")] <- "Native American/Asian"
claims$Race[which(claims$Race=="Caucasian")] <- "White"
claims$Race[which(claims$Race=="Other/Missing")] <- "Other"

#FY
claims$FY_2015 <- ifelse(claims$FY=="2015", 1, 0)
claims$FY_2016 <- ifelse(claims$FY=="2016", 1, 0)
claims$FY_2017 <- ifelse(claims$FY=="2017", 1, 0)
claims$FY_2018 <- ifelse(claims$FY=="2018", 1, 0)


```

# Example of Duplicate Claim Numbers

```{r}
head(table(claims$CLAIM_NUMBER))
#201506250785900 201506251954000 201506330015100 201506331570200 201506332414000 201506351462700 
#              5               1               2               3               1               5 

claims[which(claims$CLAIM_NUMBER=="201506250785900"),]

```

# Overall

## Claim level data

```{r}
claim_level <- claims[!duplicated(claims[,c("CLAIM_NUMBER")]),]

#total cost per claim
totc <- claims[!duplicated(claims[,c("CLAIM_NUMBER", "proc_code")]), c("CLAIM_NUMBER", "AMOUNT_PAID")] %>%
  dplyr::group_by(CLAIM_NUMBER) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
claim_level$Total_Cost <- totc$Total_Cost

dim(claim_level)
#62955    53

#total cost per claim
summary(claim_level$Total_Cost)
mean(claim_level$Total_Cost)
sd(claim_level$Total_Cost)


#CDT
table(claim_level$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level$CDT_category, exclude = "ifany")), 3)
```


## Patient level

```{r}
patient_level <- claims[!duplicated(claims[,c("SRECIP")]),]

dim(patient_level)

#age
summary(patient_level$age_at_procedure)
mean(patient_level$age_at_procedure)
sd(patient_level$age_at_procedure)

#age category
table(patient_level$age_cat, exclude = "ifany")
round(prop.table(table(patient_level$age_cat, exclude = "ifany")),3)

#race
table(patient_level$Race)
round(prop.table(table(patient_level$Race)),3)

#citizen
table(patient_level$Overall_Citizen)
round(prop.table(table(patient_level$Overall_Citizen)),3)

#region
table(patient_level$Overall_Region, exclude = "if any")
round(prop.table(table(patient_level$Overall_Region, exclude = "if any")),3)

#HPD
table(patient_level$HEALTH_PLANNING_DISTRICT, exclude = "if any")
round(prop.table(table(patient_level$HEALTH_PLANNING_DISTRICT, exclude = "if any")),3)

#HPR
table(patient_level$HEALTH_PLANNING_REGION, exclude = "if any")
round(prop.table(table(patient_level$HEALTH_PLANNING_REGION, exclude = "if any")),3)

#######################################################################################

# Cross tabulating variables between claims and eligibility

##age category
table(patient_level$age_cat, patient_level$age_cat_eligibility)
patient_level[which(patient_level$age_cat!=patient_level$age_cat_eligibility),c("CLAIM_NUMBER", "proc_code", "SRECIP", "age_at_procedure", "Overall_Age_at_earliest_enrollment", "age_cat", "age_cat_eligibility")]
length(which(patient_level$age_cat!=patient_level$age_cat_eligibility))
#745
acdat <- patient_level[which(patient_level$age_cat!=patient_level$age_cat_eligibility),c("CLAIM_NUMBER", "proc_code", "SRECIP", "age_at_procedure", "Overall_Age_at_earliest_enrollment", "age_cat", "age_cat_eligibility")]
hist(acdat$age_at_procedure-acdat$Overall_Age_at_earliest_enrollment)
acdat[which(abs(acdat$age_at_procedure-acdat$Overall_Age_at_earliest_enrollment)>5),]

## race
table(patient_level$Race, patient_level$Overall_Race)
patient_level[which(patient_level$Race!=patient_level$Overall_Race),c("CLAIM_NUMBER", "proc_code", "SRECIP", "Race", "Overall_Race")]
length(which(patient_level$Race!=patient_level$Overall_Race))
#1286
```



# 2015

## Claim level

```{r}
claims_2015 <- claims[which(claims$FY_2015==1),]

claim_level_2015 <- claims_2015[!duplicated(claims_2015[,c("CLAIM_NUMBER")]),]

#total cost per claim
totc <- claims_2015[!duplicated(claims_2015[,c("CLAIM_NUMBER", "proc_code")]), c("CLAIM_NUMBER", "AMOUNT_PAID")] %>%
  dplyr::group_by(CLAIM_NUMBER) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
claim_level_2015$Total_Cost <- totc$Total_Cost

dim(claim_level_2015)
#4533   53

#total cost per claim
summary(claim_level_2015$Total_Cost)
mean(claim_level_2015$Total_Cost)
sd(claim_level_2015$Total_Cost)


#CDT
table(claim_level_2015$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2015$CDT_category, exclude = "ifany")), 3)

```


## Patient level

```{r}
patient_2015 <- claims[which(claims$FY_2015==1),]

patient_level_2015 <- patient_2015[!duplicated(patient_2015[,c("SRECIP")]),]

#age
summary(patient_level_2015$age_at_procedure)
mean(patient_level_2015$age_at_procedure)
sd(patient_level_2015$age_at_procedure)

#age category
table(patient_level_2015$age_cat, exclude = "ifany")
round(prop.table(table(patient_level_2015$age_cat, exclude = "ifany")),3)

#race
table(patient_level_2015$Race)
round(prop.table(table(patient_level_2015$Race)),3)

#citizen
table(patient_level_2015$Overall_Citizen)
round(prop.table(table(patient_level_2015$Overall_Citizen)),3)

#region
table(patient_level_2015$Overall_Region, exclude = "if any")
round(prop.table(table(patient_level_2015$Overall_Region, exclude = "if any")),3)

#HPD
table(patient_level_2015$HEALTH_PLANNING_DISTRICT, exclude = "if any")
round(prop.table(table(patient_level_2015$HEALTH_PLANNING_DISTRICT, exclude = "if any")),3)

#HPR
table(patient_level_2015$HEALTH_PLANNING_REGION, exclude = "if any")
round(prop.table(table(patient_level_2015$HEALTH_PLANNING_REGION, exclude = "if any")),3)

```


# 2016

## Claim level

```{r}
claims_2016 <- claims[which(claims$FY_2016==1),]

claim_level_2016 <- claims_2016[!duplicated(claims_2016[,c("CLAIM_NUMBER")]),]

#total cost per claim
totc <- claims_2016[!duplicated(claims_2016[,c("CLAIM_NUMBER", "proc_code")]), c("CLAIM_NUMBER", "AMOUNT_PAID")] %>%
  dplyr::group_by(CLAIM_NUMBER) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
claim_level_2016$Total_Cost <- totc$Total_Cost

dim(claim_level_2016)
#16602    53

#total cost per claim
summary(claim_level_2016$Total_Cost)
mean(claim_level_2016$Total_Cost)
sd(claim_level_2016$Total_Cost)


#CDT
table(claim_level_2016$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2016$CDT_category, exclude = "ifany")), 3)

```


## Patient level

```{r}
patient_2016 <- claims[which(claims$FY_2016==1),]

patient_level_2016 <- patient_2016[!duplicated(patient_2016[,c("SRECIP")]),]

#age
summary(patient_level_2016$age_at_procedure)
mean(patient_level_2016$age_at_procedure)
sd(patient_level_2016$age_at_procedure)

#age category
table(patient_level_2016$age_cat, exclude = "ifany")
round(prop.table(table(patient_level_2016$age_cat, exclude = "ifany")),3)

#race
table(patient_level_2016$Race)
round(prop.table(table(patient_level_2016$Race)),3)

#citizen
table(patient_level_2016$Overall_Citizen)
round(prop.table(table(patient_level_2016$Overall_Citizen)),3)

#region
table(patient_level_2016$Overall_Region, exclude = "if any")
round(prop.table(table(patient_level_2016$Overall_Region, exclude = "if any")),3)

#HPD
table(patient_level_2016$HEALTH_PLANNING_DISTRICT, exclude = "if any")
round(prop.table(table(patient_level_2016$HEALTH_PLANNING_DISTRICT, exclude = "if any")),3)

#HPR
table(patient_level_2016$HEALTH_PLANNING_REGION, exclude = "if any")
round(prop.table(table(patient_level_2016$HEALTH_PLANNING_REGION, exclude = "if any")),3)

```


# 2017

## Claim level

```{r}
claims_2017 <- claims[which(claims$FY_2017==1),]

claim_level_2017 <- claims_2017[!duplicated(claims_2017[,c("CLAIM_NUMBER")]),]

#total cost per claim
totc <- claims_2017[!duplicated(claims_2017[,c("CLAIM_NUMBER", "proc_code")]), c("CLAIM_NUMBER", "AMOUNT_PAID")] %>%
  dplyr::group_by(CLAIM_NUMBER) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
claim_level_2017$Total_Cost <- totc$Total_Cost

dim(claim_level_2017)
#21649    53

#total cost per claim
summary(claim_level_2017$Total_Cost)
mean(claim_level_2017$Total_Cost)
sd(claim_level_2017$Total_Cost)


#CDT
table(claim_level_2017$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2017$CDT_category, exclude = "ifany")), 3)

```


## Patient level

```{r}
patient_2017 <- claims[which(claims$FY_2017==1),]

patient_level_2017 <- patient_2017[!duplicated(patient_2017[,c("SRECIP")]),]

#age
summary(patient_level_2017$age_at_procedure)
mean(patient_level_2017$age_at_procedure)
sd(patient_level_2017$age_at_procedure)

#age category
table(patient_level_2017$age_cat, exclude = "ifany")
round(prop.table(table(patient_level_2017$age_cat, exclude = "ifany")),3)

#race
table(patient_level_2017$Race)
round(prop.table(table(patient_level_2017$Race)),3)

#citizen
table(patient_level_2017$Overall_Citizen)
round(prop.table(table(patient_level_2017$Overall_Citizen)),3)

#region
table(patient_level_2017$Overall_Region, exclude = "if any")
round(prop.table(table(patient_level_2017$Overall_Region, exclude = "if any")),3)

#HPD
table(patient_level_2017$HEALTH_PLANNING_DISTRICT, exclude = "if any")
round(prop.table(table(patient_level_2017$HEALTH_PLANNING_DISTRICT, exclude = "if any")),3)

#HPR
table(patient_level_2017$HEALTH_PLANNING_REGION, exclude = "if any")
round(prop.table(table(patient_level_2017$HEALTH_PLANNING_REGION, exclude = "if any")),3)

```


# 2018

## Claim level

```{r}
claims_2018 <- claims[which(claims$FY_2018==1),]

claim_level_2018 <- claims_2018[!duplicated(claims_2018[,c("CLAIM_NUMBER")]),]

#total cost per claim
totc <- claims_2018[!duplicated(claims_2018[,c("CLAIM_NUMBER", "proc_code")]), c("CLAIM_NUMBER", "AMOUNT_PAID")] %>%
  dplyr::group_by(CLAIM_NUMBER) %>%
  dplyr::summarize(Total_Cost = sum(as.numeric(AMOUNT_PAID)))
claim_level_2018$Total_Cost <- totc$Total_Cost

dim(claim_level_2018)
#22076    53

#total cost per claim
summary(claim_level_2018$Total_Cost)
mean(claim_level_2018$Total_Cost)
sd(claim_level_2018$Total_Cost)


#CDT
table(claim_level_2018$CDT_category, exclude = "ifany")
round(prop.table(table(claim_level_2018$CDT_category, exclude = "ifany")), 3)

```


## Patient level

```{r}
patient_2018 <- claims[which(claims$FY_2018==1),]

patient_level_2018 <- patient_2018[!duplicated(patient_2018[,c("SRECIP")]),]

#age
summary(patient_level_2018$age_at_procedure)
mean(patient_level_2018$age_at_procedure)
sd(patient_level_2018$age_at_procedure)

#age category
table(patient_level_2018$age_cat, exclude = "ifany")
round(prop.table(table(patient_level_2018$age_cat, exclude = "ifany")),3)

#race
table(patient_level_2018$Race)
round(prop.table(table(patient_level_2018$Race)),3)

#citizen
table(patient_level_2018$Overall_Citizen)
round(prop.table(table(patient_level_2018$Overall_Citizen)),3)

#region
table(patient_level_2018$Overall_Region, exclude = "if any")
round(prop.table(table(patient_level_2018$Overall_Region, exclude = "if any")),3)

#HPD
table(patient_level_2018$HEALTH_PLANNING_DISTRICT, exclude = "if any")
round(prop.table(table(patient_level_2018$HEALTH_PLANNING_DISTRICT, exclude = "if any")),3)

#HPR
table(patient_level_2018$HEALTH_PLANNING_REGION, exclude = "if any")
round(prop.table(table(patient_level_2018$HEALTH_PLANNING_REGION, exclude = "if any")),3)

```

# Intersection of claim numbers across years

```{r}
length(intersect(claim_level_2015$CLAIM_NUMBER, claim_level_2016$CLAIM_NUMBER)) #14
length(intersect(claim_level_2015$CLAIM_NUMBER, claim_level_2017$CLAIM_NUMBER)) #0
length(intersect(claim_level_2015$CLAIM_NUMBER, claim_level_2018$CLAIM_NUMBER)) #0

length(intersect(claim_level_2016$CLAIM_NUMBER, claim_level_2017$CLAIM_NUMBER)) #5
length(intersect(claim_level_2016$CLAIM_NUMBER, claim_level_2018$CLAIM_NUMBER)) #0

length(intersect(claim_level_2017$CLAIM_NUMBER, claim_level_2018$CLAIM_NUMBER)) #11
```

# Intersection of srecip across years

```{r}
length(intersect(patient_level_2015$SRECIP, patient_level_2016$SRECIP)) #602
length(intersect(patient_level_2015$SRECIP, patient_level_2017$SRECIP)) #88
length(intersect(patient_level_2015$SRECIP, patient_level_2018$SRECIP)) #81

length(intersect(patient_level_2016$SRECIP, patient_level_2017$SRECIP)) #964
length(intersect(patient_level_2016$SRECIP, patient_level_2018$SRECIP)) #281

length(intersect(patient_level_2017$SRECIP, patient_level_2018$SRECIP)) #1108
```

