---
title: "Creating dental visit type responses"
author: "Spiro Stilianoudakis"
date: "12/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
library(sas7bdat)
library(lubridate)
library(tidyr)
library(tableone)
library(pscl)
library(pROC)
library(DMwR)
library(caret)
library(rattle)
library(randomForest)
library(reprtree)
library(car)
library(ResourceSelection)
library(pscl)
library(countreg)
library("lmtest")
```

# Read in Eligibility data

```{r}
eligibility <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/ffs_mco_2015_2016_2017_2018.rds")

dim(eligibility) #103204    156
length(unique(eligibility$srecip)) #103204

#keeping only necessary variables
vars <- c("srecip", 
          "Overall_Age_at_earliest_enrollment",
          "Overall_Citizen",
          "Overall_Region",
          "Overall_Race",
          "Overall_R_FIPS",
          "HEALTH_PLANNING_DISTRICT",
          "HEALTH_PLANNING_REGION",
          "months_enrolled",
          "months_enrolled_cat",
          "months_enrolled_2015",
          #"months_enrolled_2015_cat",
          "months_enrolled_2016",
          #"months_enrolled_2016_cat",
          "months_enrolled_2017",
          #"months_enrolled_2017_cat",
          "months_enrolled_2018",
          #"months_enrolled_2018_cat",
          "policymaturation",
          "FY2015",
          "FY2016",
          "FY2017",
          "FY2018")
eligibility <- eligibility[, which(names(eligibility) %in% vars)]
dim(eligibility) 
#103204     18
#80680    18
#103985     12
```

# Read in Claims data

```{r}
#claims <- read.xlsx("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/Pregnant_claims_2015_2018.xlsx",
#                    sheet = "Pregnant_claims_2015_2018",
#                    startRow = 1,
#                    colNames = TRUE,
#                    na.strings = "",
#                    detectDates = TRUE)
#dim(claims) #184976     41

unique_claims <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/unique_claims.rds")
```

# Creating response vector based on if patients (SRECIP) in eligibility are in claims

```{r}
mydata <- eligibility

#mydata$dental_visit <- as.factor(ifelse(eligibility$srecip %in% unique(claims$SRECIP), "Yes", "No"))

mydata$dental_visit <- as.factor(ifelse(eligibility$srecip %in% unique_claims$SRECIP, "Yes", "No"))

table(mydata$dental_visit)
#   No   Yes 
#86313 16891 
#   No   Yes 
#65341 15339 
#   No   Yes 
#86982 17003 
prop.table(table(mydata$dental_visit))
#       No       Yes 
#0.8363339 0.1636661 
#       No       Yes 
#0.8098785 0.1901215 
#      No      Yes 
#0.836486 0.163514 
```

# Creating different dental type variables according to first dental visit

## 1. If preventative then list as preventative
## 2. If treatment then list as treatment
## 3. if diagnostic and preventative list as preventative
## 4. if diagnostic and treatment list as treatment
## 5. if diagnostic and no other type list as diagnostic
## 6. if all happening in one list as all

```{r}
firstVisit <- unique_claims %>%
    dplyr::select(SRECIP, CDT_category, SERVICE_DATE) %>%
    mutate(SERVICE_DATE2 = mdy(unique_claims$SERVICE_DATE)) %>%
    group_by(SRECIP) %>%
    arrange(SRECIP,SERVICE_DATE2) %>%
    filter(row_number()==1)
firstVisit <- as.data.frame(firstVisit)
dim(firstVisit)
#16891     4
#15339     9
#17003     4
  
followupVisit <- unique_claims %>%
    dplyr::select(SRECIP, CDT_category, SERVICE_DATE) %>%
    mutate(SERVICE_DATE2 = lubridate::mdy(unique_claims$SERVICE_DATE)) %>%
    group_by(SRECIP) %>%
    arrange(SRECIP,SERVICE_DATE2) %>%
    filter(row_number()!=1) %>%
    filter(SERVICE_DATE2 == min(SERVICE_DATE2))
followupVisit <- as.data.frame(followupVisit)
followupVisit$CDT_category <- as.character(followupVisit$CDT_category)
dim(followupVisit)
#44700     4
#40451     5
#45016     4
length(unique(followupVisit$SRECIP))
#16298
#14809
#16407

SameDayVisit <- numeric()
for(i in 1:length(followupVisit$SRECIP)){
  d <- firstVisit$SERVICE_DATE[firstVisit$SRECIP==followupVisit$SRECIP[i]]
  
  SameDayVisit[i] <- ifelse(d==followupVisit$SERVICE_DATE[i],1,0)
}
followupVisit$SameDayVisit <- SameDayVisit
followupVisit2 <- followupVisit[-which(followupVisit$SameDayVisit==0),]
dim(followupVisit2)
#39291     5
#35479     5
#39571     5
length(unique(followupVisit2$SRECIP))
#14481
#13128
#14577


followupPREVENTIVE <- numeric()
followupTREATMENT <- numeric()
followupDIAGNOSTIC <- numeric()
followupALL <- numeric()
for(i in 1:length(firstVisit$SRECIP)){
  d <- followupVisit2 %>% filter(SRECIP==firstVisit$SRECIP[i])
  cdt <- names(table(d$CDT_category))
  
  if(nrow(d)==0){
    followupPREVENTIVE[i] <- NA
    followupTREATMENT[i] <- NA
    followupDIAGNOSTIC[i] <- NA
    followupALL[i] <- NA
  }else{
    followupPREVENTIVE[i] <- ifelse((firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]=="PREVENTIVE") |
                                                 ("PREVENTIVE" %in% cdt),1,0)
    followupTREATMENT[i] <- ifelse((firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]!="PREVENTIVE" &
                                                 firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]!="DIAGNOSTIC") &
                                                 !("PREVENTIVE" %in% cdt) & !("DIAGNOSTIC" %in% cdt),1,0)
    followupDIAGNOSTIC[i] <- ifelse((firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]=="DIAGNOSTIC") &
                                                 (length(cdt)==1) &
                                                 ("DIAGNOSTIC" %in% cdt),1,0)
    followupALL[i] <- ifelse(length(unique(as.character(firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]),
                                              cdt))==7,1,0)
  }
}
firstVisit$followupPREVENTIVE <- followupPREVENTIVE
firstVisit$followupTREATMENT <- followupTREATMENT
firstVisit$followupDIAGNOSTIC <- followupDIAGNOSTIC
firstVisit$followupALL <- followupALL

#mutually exclusive?
length(which(rowSums(firstVisit[,c(5:8)])>1))
#0

firstVisit$NewDVType <- ifelse(firstVisit$followupPREVENTIVE==1,"PREVENTIVE",
                               ifelse(firstVisit$followupTREATMENT==1,"TREATMENT",
                                      ifelse(firstVisit$followupDIAGNOSTIC==1,"DIAGNOSTIC","ALL")))

#code those that didn't have multiple services as whatever the first service was
firstVisit$NewDVType[is.na(firstVisit$NewDVType)] <- as.character(firstVisit$CDT_category[is.na(firstVisit$NewDVType)])

table(firstVisit$NewDVType)
#                         ALL                   DIAGNOSTIC                  ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER                 PERIODONTICS 
#                        2725                         7484                           55                          148                          203                           76 
#                  PREVENTIVE                  RESTORATIVE                    TREATMENT 
#                        5310                          168                          722 

#                         ALL                   DIAGNOSTIC                  ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER                 PERIODONTICS 
#                        2480                         6816                           49                          129                          182                           64 
#                  PREVENTIVE                  RESTORATIVE                    TREATMENT 
#                        4802                          154                          663 

#                         ALL                   DIAGNOSTIC                  ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER                 PERIODONTICS 
#                        2742                         7537                           56                          148                          203                           76 
#                  PREVENTIVE                  RESTORATIVE                    TREATMENT 
#                        5345                          170                          726 

prop.table(table(firstVisit$NewDVType))
#                         ALL                   DIAGNOSTIC                  ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER                 PERIODONTICS 
#                 0.161265659                  0.443274716                  0.003293536                  0.008704346                  0.011939070                  0.004469799 
#                  PREVENTIVE                  RESTORATIVE                    TREATMENT 
#                 0.314356290                  0.009998236                  0.042698347 
                 
#some categories outside of d,p,t, or a because they had some other service only once











ids <- unique(unique_claims$SRECIP)
for(i in 1:length(ids)){
  
  srecipData <- unique_claims[which(unique_claims$SRECIP==ids[i]),]
  
  srecipData <- srecipData %>%
    mutate(SERVICE_DATE = mdy(srecipData$SERVICE_DATE),
           CDT_category=as.character(CDT_category)) %>%
    arrange(SERVICE_DATE) %>%
    filter(SERVICE_DATE==min(SERVICE_DATE))
  
  table(srecipData$CDT_category)
}

unique_claims$CDT_category2 <- as.character(unique_claims$CDT_category)
unique_claims$CDT_category2[which(unique_claims$CDT_category2!="DIAGNOSTIC" & unique_claims$CDT_category2!="PREVENTIVE")] <- "TREATMENT"
table(unique_claims$CDT_category2, exclude = "ifany")

cdts <- sapply(unique(unique_claims$SRECIP),function(x){
  srecipData <- unique_claims[which(unique_claims$SRECIP==x),]
  
  srecipData <- srecipData %>%
    mutate(SERVICE_DATE = mdy(srecipData$SERVICE_DATE),
           CDT_category2=as.character(CDT_category2)) %>%
    arrange(SERVICE_DATE) %>%
    filter(SERVICE_DATE==min(SERVICE_DATE))
  
  #return(names(table(srecipData$CDT_category2)))
  n <- names(table(srecipData$CDT_category2))
  if( length(n)==3 ){
    return("ALL")
  }else if(length(n)==2 & ("PREVENTIVE" %in% n) & (!("TREATMENT" %in% n))){
    return("PREVENTIVE")
  }else if(length(n)==2 & ("TREATMENT" %in% n) & (!("PREVENTIVE" %in% n))){
    return("TREATMENT")
  }else if(length(n)==2 & ("TREATMENT" %in% n) & ("PREVENTIVE" %in% n)){
    return("PREVENTIVE & TREATMENT")
  }else if(length(n)==1 & ("DIAGNOSTIC" %in% n)){
    return("DIAGNOSTIC")
  }else if(length(n)==1 & ("PREVENTIVE" %in% n)){
    return("PREVENTIVE")
  }else if(length(n)==1 & ("TREATMENT" %in% n)){
    return("TREATMENT")
  }else{return("UNKNOWN")}
  
  
  }
  )

table(cdts, exclude = "ifany")
#ALL             DIAGNOSTIC             PREVENTIVE PREVENTIVE & TREATMENT              TREATMENT 
#897                   7537                   4409                     39                   4121 
which(cdts=="PREVENTIVE & TREATMENT")

x <- unique(unique_claims$SRECIP)[1463];srecipData <- unique_claims[which(unique_claims$SRECIP==x),]
srecipData <- srecipData %>%
  mutate(SERVICE_DATE = mdy(srecipData$SERVICE_DATE),
         CDT_category2=as.character(CDT_category2)) %>%
  arrange(SERVICE_DATE) %>%
  filter(SERVICE_DATE==min(SERVICE_DATE));n=names(table(srecipData$CDT_category2));srecipData
```

