---
title: "Creating dental visit type responses"
author: "Spiro Stilianoudakis"
date: "12/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
library(sas7bdat)
library(lubridate)
library(tidyr)
library(tableone)
library(pscl)
library(pROC)
library(DMwR)
library(caret)
library(rattle)
library(randomForest)
library(reprtree)
library(car)
library(ResourceSelection)
library(pscl)
library(countreg)
library("lmtest")
```

# Read in Eligibility data

```{r}
eligibility <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/ffs_mco_2015_2016_2017_2018.rds")

dim(eligibility) #103204    156
length(unique(eligibility$srecip)) #103204

#keeping only necessary variables
vars <- c("srecip", 
          "Overall_Age_at_earliest_enrollment",
          "Overall_Citizen",
          "Overall_Region",
          "Overall_Race",
          "Overall_R_FIPS",
          "HEALTH_PLANNING_DISTRICT",
          "HEALTH_PLANNING_REGION",
          "months_enrolled",
          "months_enrolled_cat",
          "months_enrolled_2015",
          #"months_enrolled_2015_cat",
          "months_enrolled_2016",
          #"months_enrolled_2016_cat",
          "months_enrolled_2017",
          #"months_enrolled_2017_cat",
          "months_enrolled_2018",
          #"months_enrolled_2018_cat",
          "policymaturation",
          "FY2015",
          "FY2016",
          "FY2017",
          "FY2018")
eligibility <- eligibility[, which(names(eligibility) %in% vars)]
dim(eligibility) 
#103204     18
#80680    18
```

# Read in Claims data

```{r}
#claims <- read.xlsx("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/Pregnant_claims_2015_2018.xlsx",
#                    sheet = "Pregnant_claims_2015_2018",
#                    startRow = 1,
#                    colNames = TRUE,
#                    na.strings = "",
#                    detectDates = TRUE)
#dim(claims) #184976     41

unique_claims <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/unique_claims.rds")
```

# Creating response vector based on if patients (SRECIP) in eligibility are in claims

```{r}
mydata <- eligibility

#mydata$dental_visit <- as.factor(ifelse(eligibility$srecip %in% unique(claims$SRECIP), "Yes", "No"))

mydata$dental_visit <- as.factor(ifelse(eligibility$srecip %in% unique_claims$SRECIP, "Yes", "No"))

table(mydata$dental_visit)
#   No   Yes 
#86313 16891 
#   No   Yes 
#65341 15339 
prop.table(table(mydata$dental_visit))
#       No       Yes 
#0.8363339 0.1636661 
#       No       Yes 
#0.8098785 0.1901215 
```

# Creating different dental type variables according to first dental visit

## 1. If preventative then list as preventative
## 2. If treatment then list as treatment
## 3. if diagnostic followed by preventative list as preventative
## 4. if diagnostic followed by treatment list as treatment
## 5. if diagnostic and no other type list as diagnostic
## 6. if all happening in one list as all

```{r}
firstVisit <- unique_claims %>%
    dplyr::select(SRECIP, CDT_category, SERVICE_DATE) %>%
    mutate(SERVICE_DATE2 = mdy(unique_claims$SERVICE_DATE)) %>%
    group_by(SRECIP) %>%
    arrange(SRECIP,SERVICE_DATE2) %>%
    filter(row_number()==1)
firstVisit <- as.data.frame(firstVisit)
dim(firstVisit)
#16891     4
#15339     9
  
followupVisit <- unique_claims %>%
    dplyr::select(SRECIP, CDT_category, SERVICE_DATE) %>%
    mutate(SERVICE_DATE2 = lubridate::mdy(unique_claims$SERVICE_DATE)) %>%
    group_by(SRECIP) %>%
    arrange(SRECIP,SERVICE_DATE2) %>%
    filter(row_number()!=1) %>%
    filter(SERVICE_DATE2 == min(SERVICE_DATE2))
followupVisit <- as.data.frame(followupVisit)
followupVisit$CDT_category <- as.character(followupVisit$CDT_category)
dim(followupVisit)
#44700     4
#40451     5
length(unique(followupVisit$SRECIP))
#16298
#14809

SameDayVisit <- numeric()
for(i in 1:length(followupVisit$SRECIP)){
  d <- firstVisit$SERVICE_DATE[firstVisit$SRECIP==followupVisit$SRECIP[i]]
  
  SameDayVisit[i] <- ifelse(d==followupVisit$SERVICE_DATE[i],1,0)
}
followupVisit$SameDayVisit <- SameDayVisit
followupVisit2 <- followupVisit[-which(followupVisit$SameDayVisit==0),]
dim(followupVisit2)
#39291     5
#35479     5
length(unique(followupVisit2$SRECIP))
#14481
#13128


followupPREVENTIVE <- numeric()
followupTREATMENT <- numeric()
followupDIAGNOSTIC <- numeric()
followupALL <- numeric()
for(i in 1:length(firstVisit$SRECIP)){
  d <- followupVisit2 %>% filter(SRECIP==firstVisit$SRECIP[i])
  cdt <- names(table(d$CDT_category))
  
  if(nrow(d)==0){
    followupPREVENTIVE[i] <- NA
    followupTREATMENT[i] <- NA
    followupDIAGNOSTIC[i] <- NA
    followupALL[i] <- NA
  }else{
    followupPREVENTIVE[i] <- ifelse((firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]=="PREVENTIVE") |
                                                 ("PREVENTIVE" %in% cdt),1,0)
    followupTREATMENT[i] <- ifelse((firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]!="PREVENTIVE" &
                                                 firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]!="DIAGNOSTIC") &
                                                 !("PREVENTIVE" %in% cdt) & !("DIAGNOSTIC" %in% cdt),1,0)
    followupDIAGNOSTIC[i] <- ifelse((firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]=="DIAGNOSTIC") &
                                                 (length(cdt)==1) &
                                                 ("DIAGNOSTIC" %in% cdt),1,0)
    followupALL[i] <- ifelse(length(unique(as.character(firstVisit$CDT_category[firstVisit$SRECIP==firstVisit$SRECIP[i]]),
                                              cdt))==7,1,0)
  }
}
firstVisit$followupPREVENTIVE <- followupPREVENTIVE
firstVisit$followupTREATMENT <- followupTREATMENT
firstVisit$followupDIAGNOSTIC <- followupDIAGNOSTIC
firstVisit$followupALL <- followupALL

#mutually exclusive?
length(which(rowSums(firstVisit[,c(5:8)])>1))
#0

firstVisit$NewDVType <- ifelse(firstVisit$followupPREVENTIVE==1,"PREVENTIVE",
                               ifelse(firstVisit$followupTREATMENT==1,"TREATMENT",
                                      ifelse(firstVisit$followupDIAGNOSTIC==1,"DIAGNOSTIC","ALL")))

#code those that didn't have multiple services as whatever the first service was
firstVisit$NewDVType[is.na(firstVisit$NewDVType)] <- as.character(firstVisit$CDT_category[is.na(firstVisit$NewDVType)])

table(firstVisit$NewDVType)
#                         ALL                   DIAGNOSTIC                  ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER                 PERIODONTICS 
#                        2725                         7484                           55                          148                          203                           76 
#                  PREVENTIVE                  RESTORATIVE                    TREATMENT 
#                        5310                          168                          722 

#                         ALL                   DIAGNOSTIC                  ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER                 PERIODONTICS 
#                        2480                         6816                           49                          129                          182                           64 
#                  PREVENTIVE                  RESTORATIVE                    TREATMENT 
#                        4802                          154                          663 

prop.table(table(firstVisit$NewDVType))

#some categories outside of d,p,t, or a because they had some other service only once
```

