---
title: "Identifying unique claims ("services")"
author: "Spiro Stilianoudakis"
date: "9/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
library(sas7bdat)
library(lubridate)
library(tidyr)
```

# Set working directory

```{r}
setwd("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data")
```

# Reading in pregnancy claims data

```{r}
claims <- read.xlsx("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/Pregnant_claims_2015_2018.xlsx",
                    sheet = "Pregnant_claims_2015_2018",
                    startRow = 1,
                    colNames = TRUE,
                    na.strings = "",
                    detectDates = TRUE)

claims <- claims[order(claims$SRECIP, decreasing = FALSE),]

dim(claims)
#184976     41

length(unique(claims$SRECIP)) #17485
length(unique(claims$CLAIM_NUMBER)) #64830
```

# Reading in cleaned eligibility data

```{r}
eligibility <- readRDS("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/ffs_mco_2015_2016_2017_2018.rds")
dim(eligibility) 
#103204    156
#80680   164
```

# Joining dental claims with eligibility data

```{r}
cols <- c("srecip", "Overall_Region", "HEALTH_PLANNING_DISTRICT", "HEALTH_PLANNING_REGION", "Overall_Citizen", "Overall_Race", "Overall_Age_at_earliest_enrollment", "months_enrolled", "Overall_R_FIPS")

claims <- left_join(claims, eligibility[,which(names(eligibility) %in% cols)], by = c("SRECIP" = "srecip"))

#remove claims that are not in eligibility
claims <- claims[which(claims$SRECIP %in% eligibility$srecip),]
dim(claims) 
#179518     47
#165134     49

```

#creating variables

##FY based on FY variable in claims

```{r}
claims$FY_2015 <- ifelse(claims$FY=="2015", 1, 0)
claims$FY_2016 <- ifelse(claims$FY=="2016", 1, 0)
claims$FY_2017 <- ifelse(claims$FY=="2017", 1, 0)
claims$FY_2018 <- ifelse(claims$FY=="2018", 1, 0)

```

##create age category from eligibility

```{r}

#claims$age_cat_eligibility <- ifelse(claims$Overall_Age_at_earliest_enrollment < 21, "<21",
#                                   ifelse(claims$Overall_Age_at_earliest_enrollment>= 21 & claims$Overall_Age_at_earliest_enrollment < 31, "21-30",
#                                          ifelse(claims$Overall_Age_at_earliest_enrollment >= 31 & claims$Overall_Age_at_earliest_enrollment < 41, "31-40",
#                                                 ifelse(claims$Overall_Age_at_earliest_enrollment >= 41 & claims$Overall_Age_at_earliest_enrollment < 51, "41-50", ">50"))))
#claims$age_cat_eligibility <- factor(claims$age_cat_eligibility, levels=c("<21", "21-30", "31-40", "41-50", ">50"))

claims$age_cat_eligibility <- ifelse(claims$Overall_Age_at_earliest_enrollment < 30, "under 30", "over 30")
claims$age_cat_eligibility <- factor(claims$age_cat_eligibility, levels=c("under 30", "over 30"))

```

##recategorizing race

```{r}
claims$Overall_Race[which(claims$Overall_Race=="Hispanic" |
                             claims$Overall_Race=="Native American/Asian" |
                             claims$Overall_Race=="Other")] <- "Other"

table(claims$Overall_Race)
#Black Other White 
#52365 16691 96078 
```

##categorizing months enrolled

```{r}
claims$months_enrolled_cat <- ifelse(claims$months_enrolled <= 10, "3-10 months", ">10 months")
claims$months_enrolled_cat <- factor(claims$months_enrolled_cat, levels=c("3-10 months", ">10 months"))
table(claims$months_enrolled_cat)
#3-10 months  >10 months 
#     102391       62743

```

##cdt category

```{r}
##D0100-D0999 DIAGNOSTIC
##D1000-D1999 PREVENTIVE
##D2000-D2999 RESTORATIVE
##D3000-D3999 ENDODONTICS
##D4000-D4999 PERIODONTICS
##D5000-D5899 PROSTHODONTICS
##D5900-D5999 MAXILLOFACIAL PROSTHETICS
##D6000-D6199 IMPLANT SERVICES
##D6200-D6999 PROSTHODONTICS
##D7000-D7999 ORAL & MAXILLOFACIAL SURGERY
##D8000-D8999 ORTHODONTICS
##D9000-D9999 ADJUNCTIVE GENERAL SERVICES

claims$CDT_category <- ifelse(claims$proc_code %in% paste0(0,c(100:999)), "DIAGNOSTIC",
                              ifelse(claims$proc_code %in% c(1000:1999), "PREVENTIVE",
                                     ifelse(claims$proc_code %in% c(2000:2999), "RESTORATIVE",
                                            ifelse(claims$proc_code %in% c(3000:3999), "ENDODONTICS",
                                                   ifelse(claims$proc_code %in% c(4000:4999), "PERIODONTICS",
                                                          ifelse(claims$proc_code %in% c(5000:5899), "PROSTHODONTICS", 
                                                                 ifelse(claims$proc_code %in% c(5900:5999), "MAXILLOFACIAL PROSTHETICS",
                                                                        ifelse(claims$proc_code %in% c(6000:6199), "IMPLANT SERVICES",
                                                                               ifelse(claims$proc_code %in% c(6200:6999), "PROSTHODONTICS",
                                                                                      ifelse(claims$proc_code %in% c(7000:7999), "ORAL & MAXILLOFACIAL SURGERY",
                                                                                             ifelse(claims$proc_code %in% c(8000:8999), "ORTHODONTICS",
                                                                                                    ifelse(claims$proc_code %in% c(9000:9999), "ADJUNCTIVE GENERAL SERVICES", "UNKNOWN"))))))))))))

claims$CDT_category[which(claims$CDT_category=="ADJUNCTIVE GENERAL SERVICES" | claims$CDT_category=="PROSTHODONTICS")] <- "OTHER"

claims$CDT_category <- factor(claims$CDT_category, levels=c("PREVENTIVE",
                                                            "DIAGNOSTIC",
                                                            "RESTORATIVE",
                                                            "PERIODONTICS",
                                                            "ENDODONTICS",
                                                            "ORAL & MAXILLOFACIAL SURGERY",
                                                            "OTHER"))

table(claims$CDT_category)
#                  PREVENTIVE                   DIAGNOSTIC                  RESTORATIVE                 PERIODONTICS 
#                       10567                        55735                        62360                         9431 
#                 ENDODONTICS ORAL & MAXILLOFACIAL SURGERY                        OTHER 
#                        8170                        14328                         4543 
```

##HPSA

```{r}
#reading in hpsa data
hpsa_data <- read.csv("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/HPSA_data.csv", 
                      header = TRUE,
                      colClasses = c("character",
                                     "character",
                                     "character",
                                     "character",
                                     "character",
                                     "character",
                                     "character",
                                     "character",
                                     "character",
                                     "character"))
dim(hpsa_data) #60 10

hpsa_fips <- c(hpsa_data$R_FIPS,
               hpsa_data$R_FIPS2,
               hpsa_data$R_FIPS3)
hpsa_fips <- hpsa_fips[-which(hpsa_fips=="")]

claims$HPSA_status <- as.factor(sapply(claims$Overall_R_FIPS, function(x){ifelse(x %in% hpsa_fips, "Yes", "No")}))
table(claims$HPSA_status)
#    No    Yes 
#122992  56526 
#    No    Yes 
#112831  52303 
prop.table(table(claims$HPSA_status))
#       No       Yes 
#0.6851235 0.3148765 
#       No       Yes 
#0.6832693 0.3167307 
```


# Identifying unique claims

## Claims with tooth number

### Removing duplicates based on: claim #, proc code, service date, tooth number

```{r}
claims_tooth <- claims[!is.na(claims$Tooth_Number),]
dim(claims_tooth) 
#118618     57
#109159     57
table(claims_tooth$Tooth_Number, exclude = "ifany")

claims_tooth <- claims_tooth[order(claims_tooth$CLAIM_NUMBER, decreasing = TRUE),]

head(claims_tooth[,c("CLAIM_NUMBER", "SRECIP", "SERVICE_DATE", "AMOUNT_PAID", "proc_code", "Tooth_Number", "billing_prov_NPI", "CDT_category", "FY_2015" ,"FY_2016" ,"FY_2017", "FY_2018")])

claims_nodup_tooth <- claims_tooth[!(duplicated(claims_tooth[,c("CLAIM_NUMBER", "proc_code", "SERVICE_DATE", "Tooth_Number")])),]
dim(claims_nodup_tooth) 
#118616    57
#109157     57

```

## Claims with no tooth number

### Removing duplicates based on: claim #, proc code, service date, amount paid

```{r}
claims_no_tooth <- claims[is.na(claims$Tooth_Number),]
dim(claims_no_tooth) 
#60900    57
#55975    57
table(claims_no_tooth$Tooth_Number, exclude = "ifany")

claims_no_tooth <- claims_no_tooth[order(claims_no_tooth$CLAIM_NUMBER, decreasing = TRUE),]

head(claims_no_tooth[,c("CLAIM_NUMBER", "SRECIP", "SERVICE_DATE", "AMOUNT_PAID", "proc_code", "Tooth_Number", "billing_prov_NPI", "CDT_category", "FY_2015" ,"FY_2016" ,"FY_2017", "FY_2018")])

claims_nodup_no_tooth <- claims_no_tooth[!(duplicated(claims_no_tooth[,c("CLAIM_NUMBER", "proc_code", "SERVICE_DATE", "AMOUNT_PAID")])),]
dim(claims_nodup_no_tooth) 
#60900    57
#55975    57

```

## Combining the two data sets

```{r}
unique_claims <- rbind.data.frame(claims_nodup_no_tooth, claims_nodup_tooth)
dim(unique_claims) 
#179516     57
#165132     57

```

# Saving the dataset

```{r}
saveRDS(unique_claims, "X:/CommonPrograms/Oral Health Services Research Core/Spiro/Claims_Project/data/unique_claims.rds")
```


